**Bayesian statistics for longitudinal studies in biomedical research**

### 2020-10-28 Manuscripts/Manuscript_AM_v1.Rmd
updated paper sections

@@

#### the _frequentist_ case for constant correlation

@@

* Section 2: Bayesian statistics as an alternative approach. Gentle presentation of Bayes theorem _with a biomedical-related example(!)_ Advantages over ANOVA and how inference works. Argue that while it is not commonly used in the biomedical arena, it is a more accurate and flexible approach.

* Section 3: Present the implementation of a spline-fitted model in R, using data simulated from [@vishwanath2009]

>>>>

- Why LMEMs are better than ANOVA

- How LMEMs (using splines) and a Bayesian analysis can be used to analyze longitudinal data

@@

#### 1.1 the _frequentist_ case for constant correlation (ANOVA limitations)

@@

#### 1.2 the case of LMEMs using splines and how they work and how they are better than rm-ANOVA

#### 1.3 Bayesian brief introduction, and compare the results of 1.2 to the results of Bayesian

* Section 2: Implementation of both LMEMs and Bayesian and their results

Present the implementation of a spline-fitted model in R, using data simulated from [@vishwanath2009]
